---
title: "Human Trafficking in the World"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: readable

---

```{r setup, include=FALSE}
dir()
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(sf)
library(tigris)
library(leaflet)
library(reshape)
library(stringr)
library(plotly)
library(tibble)
library(RColorBrewer)
library(rworldmap)
library(tidyr) 
traffick <- read.csv("globaltrafficking.csv")
state <- read.csv("states2019.csv")
cities <-read.csv("cities.csv",stringsAsFactors = FALSE)
```

Page 1
===
Column {data-width=650}
-----------------------------------------------------------------------
### Reported Trafficking Cases in Each US State (2019) - National Human Trafficking Hotline

```{r}
# Choropleth map with the amount of Reported Trafficking Cases in each state
# in the USA.
state$State <- state.abb[match(state$State, state.name)]
plot_ly(type="choropleth", 
        locations=state$State, 
        locationmode="USA-states", 
        z=state$reportedTraffickingCases,
        colorscale= "Reds") %>% 
  layout(geo=list(scope="usa"),title="Reported Trafficking <br> Cases in Each US State 2019") %>%
  colorbar(title = "Cases")

```

Page 2
===
Row {.tabset .tabset-fade}
-----------------------------------------------------------------------
### Ages of Female Human Trafficking Victims Worldwide (2002-2019) - Counter-Trafficking Data Collaborative (CTDC)

```{r}
traffick2 <- dplyr::rename(traffick,
                           Year = yearOfRegistration,
                           Source = Datasource,
                           Gender = gender,
                           Age = ageBroad,
                           Type = typeOfExploitConcatenated, 
                           Country = citizenship,
                           Organ = isOrganRemoval,
                           Labour = isForcedLabour, 
                           Sex = isSexualExploit, 
                           Child = meansOfControlUsesChildren, 
                           Prostitution = typeOfSexProstitution)
traffick3 <- filter(traffick2,Age!="-99")
traffick4<- filter(traffick3, Age!="-99", Gender=="Female")
traffick5<- filter(traffick3, Age!="-99", Gender=="Male")


#girls 

g <- ggplot(traffick4, aes(x = Age, fill = factor(Gender))) +
  geom_bar(stat = "count", fill = "#ffc4b2") +
  xlab("Age") +
  ylab("Cases") +
  scale_x_discrete(limits=c("0--8", "9--17", "18--20", "21--23", "24--26", "27--29", "30--38", "39--47", "48+"))+
  theme(axis.text.x = element_text(angle=30))+
  coord_flip() +
  labs(fill = "Gender")
g
```


### Ages of Male Human Trafficking Victims Worldwide (2002-2019) - Counter-Trafficking Data Collaborative (CTDC)
```{r}
#Boys

b <- ggplot(traffick5, aes(x = Age, fill = factor(Gender))) +
  geom_bar(stat = "count", fill = "#B1cadb") +
  xlab("Age") +
  ylab("Cases") +
  scale_x_discrete(limits=c("0--8", "9--17", "18--20", "21--23", "24--26", "27--29", "30--38", "39--47", "48+"))+
  theme(axis.text.x = element_text(angle=30))+
  coord_flip() +
  labs(fil = "Gender")
b
```


```{r}
```

Page 3
===
Column {data-width=650}
-----------------------------------------------------------------------
### Growth of Human Trafficking (2015-2019) - National Human Trafficking Hotline

```{r}
#Growth of Human Trafficking 2015-2019
type <- read.csv("type.csv")
type1 <- filter(type, Type!="0")
library(viridis)
library(hrbrthemes)
l <-ggplot(type1, aes(x=Year, y=Cases, fill=Type)) + 
      geom_area(alpha=0.8 , size=.5, colour="white") +
      scale_fill_brewer(palette="Reds") +
      theme_ipsum() + 
      ggtitle("Growth of Human Trafficking (2015-2019)")
l <- ggplotly(l)
l
```

Page 4
===
Column {data-width=650}
-----------------------------------------------------------------------
### Top Cities for Human Trafficking in the US (2017) - - National Human Trafficking Hotline

```{r}
cities1<-cities %>% separate(Geocode, c("lat", "lon"),sep = ",") 
cities1$lat<-as.numeric(cities1$lat)
cities1$lon<-as.numeric(cities1$lon)
leaflet(cities1)%>%
  addProviderTiles(providers$OpenStreetMap.HOT)%>%
  setView(lng=-98.77154031957267,lat=40.55465833108507,zoom=4)%>%
  addCircleMarkers(~lon,~lat,
             popup=paste(cities$City,"<br>","Number of Reported Cases", "<br>","Per 100,000 people:", cities$Cases), 
             weight=10,stroke=TRUE, radius= ~Cases/8, color="#bc5449",fillOpacity=.3)


```


Page 5
===
Column {data-width=650}
-----------------------------------------------------------------------

### Top 10 Countries for Human Trafficking (2002-2019) - Counter-Trafficking Data Collaborative (CTDC)

```{r}
traffick4 <- filter(traffick3, Country!="-99", Country!="00")
traffick7<- factor(traffick4$Country, levels = c("UA", "MD", "US", "ID", "BY","MM", "KH", "RO", "GH", "KG"))
df<-as.data.frame(traffick7)
barplot(table(traffick7), ylab="Cases", main="Top 10 Countries for Human Trafficking (2002-2019)", 
        ylim=c(0,10000), las=2, cex.main=1.2,cex.axis=.8, cex.lab=1, col="#A45A52", names.arg=c("Ukraine", "Un. States", "Moldova", "Indonesia", "Belarus", "Myanmar", "Cambodia", "Romania", "Ghana", "Kyrgyzstan"))


```

